\large Multi-Robot Probabilistic Mapping and Exploration

### 2018-07-12 Dissertation/Defense/defense.tex
finished defense exxcept for minor issues

% TODO: uncomment!
%\begin{frame}
%\frametitle{Numerical Example: SEH Second Floor}
%
%
%	\centering{
%		\includemedia[
%  		width=0.720\textwidth,
%  		height=0.576\textwidth,
%  		activate=pageopen,
%  		addresource=Multi-Vehicle Mapping and Exploration.mp4,
%  		flashvars={source=Multi-Vehicle Mapping and Exploration.mp4}
%		]{}{VPlayer.swf}
%		}
%
%
%\end{frame}

@@

% TODO: uncomment!
%\begin{frame}
%\frametitle{Numerical Example: SEH Second Floor}
%
%
%	\centering{
%		\includemedia[
%  		width=0.720\textwidth,
%  		height=0.576\textwidth,
%  		activate=pageopen,
%  		addresource=Multi-Vehicle Cooperative Patrol.mp4,
%  		flashvars={source=Multi-Vehicle Cooperative Patrol.mp4}
%		]{}{VPlayer.swf}
%		}
%
%
%\end{frame}

@@

%
%\section*{}
%
%\begin{frame}
%\frametitle{}
%%\center
%\center{\bf \color{blue} Single-Robot Autonomous Exploration}
%\end{frame}
%
%
%\subsection*{Single-Robot Autonomous Exploration}
%
%\begin{frame}
%\frametitle{Introduction}
%\begin{itemize}
%        	\item The environment is initially uncertain, so the robot path is initially unknown
%	\item Simultaneous localization and mapping assumes robotic actions are provided
%	\item Human interaction is common to guide the robot
%	\item Goal: develop effective policies to govern robotic motion 
%\end{itemize}
%
%\end{frame}
%
%
%\begin{frame}
%\frametitle{Problem Definition}
%\begin{itemize}
%        	\item Uncertainty-Based Exploration
%	\begin{itemize}
%		\item Main idea: choose robot motions that minimize the uncertainty of the occupancy grid map
%		\item Equivalently maximize map information gain
%	\end{itemize}
%\end{itemize}
%\begin{minipage}[t]{7.0cm}
%\begin{itemize}
%	\item Entropy
%	\begin{itemize}		
%		\item \emph{Shannon's entropy} serves as an uncertainty measure
%		\begin{align*}
%			H(P)=-P\log P-\bar{P}\log \bar{P}%-(1-P)\log(1-P)
%		\end{align*}
%		with cell occupancy probability $P$ and complement $\bar{P}=1-P$
%		\item Entropy $H$ is maximized when $P=0.5$ and minimized as $P\rightarrow0$ or $P\rightarrow1$
%	\end{itemize}
%\end{itemize}
%\end{minipage}
%\begin{minipage}[t]{3.0cm}
%\vspace*{0.5cm}
%\begin{figure}[!htbp]
%	\centerline{
%		\hspace*{1.25cm}
%   		\includegraphics[width=5.0cm]{H_Plotted_square.pdf}%\hspace*{0.1cm}
%	}
%\end{figure}
%\end{minipage}
%
%\end{frame}
%
%
%
%\begin{frame}
%\frametitle{Problem Definition}
%\begin{itemize}
%        	\item Map Information Gain Maximization
%	\begin{itemize}
%		\item Goal: choose a set of optimal future poses to maximize map information gain
%		\pause
%		\item Challenge: the complete set cannot be calculated accurately with an initially highly-uncertain environment
%		\pause
%		\item Solution: choose short-term optimal pose goals, reevaluating an updated map for the subsequent optimizations
%		\pause
%		\item The information gain considering candidate future pose $X_c$:% is
%		\begin{align*}
%			\mathcal I(X_c)&=H(P(m|X_{1:t},Z_{1:t}))-\text{E}\left[H(P(m|X_{1:t},Z_{1:t},X_c,Z_c))\right]
%		\end{align*}
%		\pause
%		\item Optimal pose $X^*_c$ satisfies
%		\begin{align*}
%			X_c^*=\argmax_{X_c}{\mathcal I(X_c)}
%		\end{align*}
%	\end{itemize}
%\end{itemize}
%
%
%\end{frame}
%
%
%
%\begin{frame}
%\frametitle{Related Work}
%\begin{itemize}
%        	\item Frontier-Based Exploration
%	\begin{itemize}
%		\item Main idea: robot moves toward boundaries between certain and uncertain space, takes measurements, then pushes back the boundaries
%		\item Non-entropy-based exploration
%		\item Heuristic
%	\end{itemize}
%	\pause
%	\item Entropy-Based Exploration
%	\begin{itemize}
%		\item Cell occupancy probabilities are inaccurate: inverse sensor model is heuristic or learned, and frequently estimated with Rao-Blackwellized particle filters
%		\item Inaccurate probabilities imply inaccurate entropy measures
%		\item Approaches use ``hallucination measurements'' to predict how future measurements \emph{might} affect the map uncertainty,
%		\begin{align*}
%			\text{E}\left[H(P(m|X_{1:t},Z_{1:t},X_c,Z_c))\right]\approx H(P(m|X_{1:t},Z_{1:t},X_c,\text{E}\left[Z_c\right]))
%		\end{align*}
%	\end{itemize}
%\end{itemize}
%
%
%\end{frame}
%
%
%\begin{frame}
%\frametitle{Direct Entropy Calculation}
%\begin{itemize}
%        	\item Instead of relying on frontiers or making assumptions about measurements, the expected map entropy is \emph{calculated directly} by the law of total expectation:
%	\begin{align*}
%		\text{E}[H(P(m|X,z))]=\int_{z_\text{min}}^{z_\text{max}}
%		H(P(m|X,z))p(z|X)dz,
%	\end{align*}
%	\item The robot pose is chosen to maximize map information gain from this expectation
%	\item Dijkstra's algorithm provides collision-free waypoints for the robot path
%	\item Smooth trajectory: constrained polynomial least squares 
%\end{itemize}
%
%
%\end{frame}
%
%
%\begin{frame}
%\frametitle{Numerical Example}
%\begin{itemize}
%        	\item A benchmark example floor plan is explored and mapped using the proposed mapping and exploration algorithms
%	\item Simulations in Robot Operating System (ROS)
%\end{itemize}
%\begin{figure}
%    \centering
%    \includegraphics[width=0.4\textwidth]{intel_clean.png}
%    \caption*{Modified Intel Research Lab floor plan form the SLAM benchmark}
%\end{figure}
%
%\end{frame}
%
%%\begin{frame}
%%\frametitle{Numerical Results}
%%	\centering{
%%	\includemovie[poster,autoplay]{0.720\textwidth}{0.576\textwidth}{../../Fig/JIRS16_simulation_speedup10x_then_speedup100x.mov}}
%%\end{frame}
%
%\begin{frame}
%\frametitle{Numerical Results}
%
%\begin{figure}[!ht]
%    \centering
%    \begin{subfigure}[t]{0.2\columnwidth}
%        \centering
%        \includegraphics[trim = {4.6cm 3.8cm 4.6cm 0}, clip, width=\textwidth]{0min.png}
%        \caption*{$t=0$ min}
%        \label{fig:IRL0min}
%    \end{subfigure}
%    \begin{subfigure}[t]{0.2\columnwidth}
%        \centering
%        \includegraphics[trim = {4.6cm 3.8cm 4.6cm 0}, clip, width=\textwidth]{5min.png}
%        \caption*{$t=5$ min}
%        \label{fig:IRL5min}
%    \end{subfigure}
%    \begin{subfigure}[t]{0.2\columnwidth}
%           \centering
%           \includegraphics[trim = {4.6cm 3.8cm 4.6cm 0}, clip, width=\textwidth]{10min.png}
%        \caption*{$t=10$ min}
%        \label{fig:IRL10min}
%    \end{subfigure}
%    \begin{subfigure}[t]{0.2\columnwidth}
%           \centering
%           \includegraphics[trim = {4.6cm 3.8cm 4.6cm 0}, clip, width=\textwidth]{15min.png}
%        \caption*{$t=15$ min}
%        \label{fig:IRL15min}
%    \end{subfigure}
%    \begin{subfigure}[t]{0.2\columnwidth}
%         \centering
%         \includegraphics[trim = {4.6cm 3.8cm 4.6cm 0}, clip, width=\textwidth]{20min.png}
%        \caption*{$t=20$ min}
%        \label{fig:IRL20min}
%    \end{subfigure}
%    \begin{subfigure}[t]{0.2\columnwidth}
%           \centering
%           \includegraphics[trim = {4.6cm 3.8cm 4.6cm 0}, clip, width=\textwidth]{25min.png}
%        \caption*{$t=25$ min}
%        \label{fig:IRL25min}
%    \end{subfigure}
%    \begin{subfigure}[t]{0.2\columnwidth}
%           \centering
%           \includegraphics[trim = {4.6cm 3.8cm 4.6cm 0}, clip, width=\textwidth]{30min.png}
%        \caption*{$t=30$ min}
%        \label{fig:IRL30min}
%    \end{subfigure}
%    \begin{subfigure}[t]{0.2\columnwidth}
%           \centering
%           \includegraphics[trim = {4.6cm 3.8cm 4.6cm 0}, clip, width=\textwidth]{35min.png}
%        \caption*{$t=35$ min}
%        \label{fig:IRL35min}
%    \end{subfigure}
%%    \begin{subfigure}[t]{0.2\columnwidth}
%%           \centering
%%           \includegraphics[trim = {4.6cm 3.8cm 4.6cm 0}, clip, width=\textwidth]{40min.png}
%%        \caption*{$t=40$ min}
%%        \label{fig:IRL40min}
%%    \end{subfigure}
%    \caption*{A robot (green) measures a room in ROS Stage simulator using modified Intel Research Lab floor plan using the proposed mapping and exploration algorithms.}
%    \label{fig:IRL}
%\end{figure}
%
%
%\end{frame}
%
%
%
%
%
%\begin{frame}
%\frametitle{Experimental Example}
%\begin{itemize}
%        	\item A pioneer ground vehicle explores a room composed of Styrofoam walls
%	\item Experiments use ROS, a Microsoft Kinect depth sensor, and Vicon Tracker for pose information
%\end{itemize}
%\begin{figure}
%	\centering
%    	\begin{subfigure}[b]{0.28\textwidth}
%        		\includegraphics[width=\textwidth]{pioneer.png}
%        		\caption*{Pioneer}
%    	\end{subfigure}    	
%	\hspace*{0.04\textwidth}
%	\begin{subfigure}[b]{0.28\textwidth}
%        		\includegraphics[width=\textwidth]{test_setup_1.jpg}
%        		\caption*{Bottom-left view}
%    	\end{subfigure}
%	\hspace*{0.03\textwidth}
%	\begin{subfigure}[b]{0.28\textwidth}
%        		\includegraphics[width=\textwidth]{test_setup_2.jpg}
%        		\caption*{Bottom-right view}
%    	\end{subfigure}
%\end{figure}
%
%\end{frame}
%
%%\begin{frame}
%%\frametitle{Experimental Results}
%%	\centering{
%%	\includemovie[poster,autoplay]{0.720\textwidth}{0.576\textwidth}{../../Fig/JIRS16_experiment_SideBySide_speedup8x.mov}}
%%\end{frame}
%
%\begin{frame}
%\frametitle{Experimental Results}
%
%\begin{figure}
%	\centering{
%    	\begin{subfigure}[b]{0.19\textwidth}
%        		\includegraphics[trim={13cm 1cm 13cm 0}, clip, width=\textwidth]{t_start.jpg}
%        		\caption*{$t=0.0$min}
%        		\label{fig:Experiment_ogm_t0}
%    	\end{subfigure}
%	\begin{subfigure}[b]{0.19\textwidth}
%        		\includegraphics[trim={13cm 1cm 13cm 0}, clip, width=\textwidth]{t_0p5min.jpg}
%        		\caption*{$t=0.5$min}
%        		\label{fig:Experiment_ogm_t0p5}
%    	\end{subfigure}    
%	\begin{subfigure}[b]{0.19\textwidth}
%        		\includegraphics[trim={13cm 1cm 13cm 0}, clip, width=\textwidth]{t_1min.jpg}
%        		\caption*{$t=1.0$min}
%        		\label{fig:Experiment_ogm_t1}
%    	\end{subfigure}
%	\begin{subfigure}[b]{0.19\textwidth}
%        		\includegraphics[trim={13cm 1cm 13cm 0}, clip, width=\textwidth]{t_1p5min.jpg}
%        		\caption*{$t=1.5$min}
%        		\label{fig:Experiment_ogm_t1p5}
%    	\end{subfigure}
%	\begin{subfigure}[b]{0.19\textwidth}
%        		\includegraphics[trim={13cm 1cm 13cm 0}, clip, width=\textwidth]{t_2min.jpg}
%        		\caption*{$t=2.0$min}
%        		\label{fig:Experiment_ogm_t2}
%    	\end{subfigure}
%		\vspace*{0.05\textwidth}
%
%	}
%	\vspace*{-1cm}
%	\centering{
%    	\begin{subfigure}[b]{0.19\textwidth}
%        		\includegraphics[trim={13cm 1cm 13cm 0}, clip, width=\textwidth]{t_2p5min.jpg}
%        		\caption*{$t=2.5$min}
%        		\label{fig:Experiment_ogm_t2p5}
%    	\end{subfigure}
%	\begin{subfigure}[b]{0.19\textwidth}
%        		\includegraphics[trim={13cm 1cm 13cm 0}, clip, width=\textwidth]{t_3min.jpg}
%        		\caption*{$t=3.0$min}
%        		\label{fig:Experiment_ogm_t3}
%    	\end{subfigure}    
%	\begin{subfigure}[b]{0.19\textwidth}
%        		\includegraphics[trim={13cm 1cm 13cm 0}, clip, width=\textwidth]{t_3p5min.jpg}
%        		\caption*{$t=3.5$min}
%        		\label{fig:Experiment_ogm_t3p5}
%    	\end{subfigure}
%	\begin{subfigure}[b]{0.19\textwidth}
%        		\includegraphics[trim={13cm 1cm 13cm 0}, clip, width=\textwidth]{t_4min.jpg}
%        		\caption*{$t=4.0$min}
%        		\label{fig:Experiment_ogm_t4}
%    	\end{subfigure}
%	\begin{subfigure}[b]{0.19\textwidth}
%        		\includegraphics[trim={13cm 1cm 13cm 0}, clip, width=\textwidth]{t_4p5min.jpg}
%        		\caption*{$t=4.5$min}
%        		\label{fig:Experiment_ogm_t4p5}
%    	\end{subfigure}
%	}
%\end{figure}
%
%\end{frame}
%
%
%
%\section*{}
%
%\begin{frame}
%\frametitle{}
%%\center
%\center{\bf \color{blue} Future Direction:\\Multi-Robot Autonomous Exploration}
%\end{frame}
%
%\subsection*{Future Direction: Multi-Robot Autonomous Exploration}
%
%\begin{frame}
%\frametitle{Proposed Topics}
%\begin{itemize}
%        	\item The ray-by-ray exact occupancy grid mapping approach in centralized probabilistic mapping
%	\item Multiple robots choosing optimal motions considering each other
%	\item Robots avoiding collisions with each other
%	\item Coverage optimization of robots from different poses
%\end{itemize}
%
%\end{frame}
%
%\begin{frame}
%\frametitle{Proposed Future Steps}
%\begin{itemize}
%        	\item Mapping:
%	\begin{itemize}
%		\item Restructure algorithms for centralized map generation
%		\item Communicate with multiple measurement sources
%	\end{itemize}
%	\item Exploration:
%	\begin{itemize}
%		\item Simplify enormous computation: bidding-based approach
%		\item Temporary theoretical map building
%		\item Collision avoidance between robots
%	\end{itemize}
%\end{itemize}
%
%\end{frame}
%
%
%
%\section*{}
%
%\begin{frame}
%\frametitle{}
%%\center
%\center{\bf \color{blue} Conclusions and Publications}
%\end{frame}
%
%
%\subsection*{Conclusions and Publications}
%
%\begin{frame}
%\frametitle{Conclusions}
%\begin{itemize}
%        	\item Proposed an occupancy grid mapping technique that uses the \emph{exact probabilistic solution}
%	\item Computational cost is reduced \emph{substantially} for \emph{real-time implementation} using probabilisitic properties and exploiting mathematical patterns
%	\item Exact mapping concepts are extended to map uncertainty to accomplish \emph{autonomous exploration}
%	\item Proposing multiple vehicles can explore an uncertain environment using a \emph{bidding}-based approach
%\end{itemize}
%\end{frame}

>>>>

% TODO: uncomment!
%\begin{frame}
%\frametitle{Numerical Example: SEH Second Floor Multi-Vehicle Autonomous Exploration}
%
%
%	\centering{
%		\includemedia[
%  		width=0.720\textwidth,
%  		height=0.576\textwidth,
%  		activate=pageopen,
%  		addresource=Multi-Vehicle Mapping and Exploration.mp4,
%  		flashvars={source=Multi-Vehicle Mapping and Exploration.mp4}
%		]{}{VPlayer.swf}
%		}
%
%
%\end{frame}

@@

% TODO: uncomment!
%\begin{frame}
%\frametitle{Numerical Example: SEH Second Floor Multi-Vehicle Autonomous Patrol}
%
%
%	\centering{
%		\includemedia[
%  		width=0.720\textwidth,
%  		height=0.576\textwidth,
%  		activate=pageopen,
%  		addresource=Multi-Vehicle Cooperative Patrol.mp4,
%  		flashvars={source=Multi-Vehicle Cooperative Patrol.mp4}
%		]{}{VPlayer.swf}
%		}
%
%
%\end{frame}

@@

\begin{frame}
\frametitle{Pioneer Ground Vehicle 2D Example}
\begin{itemize}
        	\item A pioneer ground vehicle explores a room composed of Styrofoam walls
	\item Experiments use ROS, a Microsoft Kinect depth sensor, and Vicon Tracker for pose information
\end{itemize}
\begin{figure}
	\centering
    	\begin{subfigure}[b]{0.28\textwidth}
        		\includegraphics[width=\textwidth]{pioneer.png}
        		\caption*{Pioneer}
    	\end{subfigure}    	
	\hspace*{0.04\textwidth}
	\begin{subfigure}[b]{0.28\textwidth}
        		\includegraphics[width=\textwidth]{test_setup_1.jpg}
        		\caption*{Bottom-left view}
    	\end{subfigure}
	\hspace*{0.03\textwidth}
	\begin{subfigure}[b]{0.28\textwidth}
        		\includegraphics[width=\textwidth]{test_setup_2.jpg}
        		\caption*{Bottom-right view}
    	\end{subfigure}
\end{figure}

% TODO: uncomment!
%\begin{frame}
%\frametitle{Ground Experiment Video}
%
%
%	\centering{
%		\includemedia[
%  		width=0.720\textwidth,
%  		height=0.576\textwidth,
%  		activate=pageopen,
%  		addresource=NRL_ground_test.mp4,
%  		flashvars={source=NRL_ground_test.mp4}
%		]{}{VPlayer.swf}
%		}
%
%
%\end{frame}

\begin{frame}
\frametitle{Ground Vehicle Experimental Results}

\begin{figure}
	\centering{
    	\begin{subfigure}[b]{0.19\textwidth}
        		\includegraphics[trim={13cm 1cm 13cm 0}, clip, width=\textwidth]{t_start.jpg}
        		\caption*{$t=0.0$min}
        		\label{fig:Experiment_ogm_t0}
    	\end{subfigure}
	\begin{subfigure}[b]{0.19\textwidth}
        		\includegraphics[trim={13cm 1cm 13cm 0}, clip, width=\textwidth]{t_0p5min.jpg}
        		\caption*{$t=0.5$min}
        		\label{fig:Experiment_ogm_t0p5}
    	\end{subfigure}    
	\begin{subfigure}[b]{0.19\textwidth}
        		\includegraphics[trim={13cm 1cm 13cm 0}, clip, width=\textwidth]{t_1min.jpg}
        		\caption*{$t=1.0$min}
        		\label{fig:Experiment_ogm_t1}
    	\end{subfigure}
	\begin{subfigure}[b]{0.19\textwidth}
        		\includegraphics[trim={13cm 1cm 13cm 0}, clip, width=\textwidth]{t_1p5min.jpg}
        		\caption*{$t=1.5$min}
        		\label{fig:Experiment_ogm_t1p5}
    	\end{subfigure}
	\begin{subfigure}[b]{0.19\textwidth}
        		\includegraphics[trim={13cm 1cm 13cm 0}, clip, width=\textwidth]{t_2min.jpg}
        		\caption*{$t=2.0$min}
        		\label{fig:Experiment_ogm_t2}
    	\end{subfigure}
		\vspace*{0.05\textwidth}

	}
	\vspace*{-1cm}
	\centering{
    	\begin{subfigure}[b]{0.19\textwidth}
        		\includegraphics[trim={13cm 1cm 13cm 0}, clip, width=\textwidth]{t_2p5min.jpg}
        		\caption*{$t=2.5$min}
        		\label{fig:Experiment_ogm_t2p5}
    	\end{subfigure}
	\begin{subfigure}[b]{0.19\textwidth}
        		\includegraphics[trim={13cm 1cm 13cm 0}, clip, width=\textwidth]{t_3min.jpg}
        		\caption*{$t=3.0$min}
        		\label{fig:Experiment_ogm_t3}
    	\end{subfigure}    
	\begin{subfigure}[b]{0.19\textwidth}
        		\includegraphics[trim={13cm 1cm 13cm 0}, clip, width=\textwidth]{t_3p5min.jpg}
        		\caption*{$t=3.5$min}
        		\label{fig:Experiment_ogm_t3p5}
    	\end{subfigure}
	\begin{subfigure}[b]{0.19\textwidth}
        		\includegraphics[trim={13cm 1cm 13cm 0}, clip, width=\textwidth]{t_4min.jpg}
        		\caption*{$t=4.0$min}
        		\label{fig:Experiment_ogm_t4}
    	\end{subfigure}
	\begin{subfigure}[b]{0.19\textwidth}
        		\includegraphics[trim={13cm 1cm 13cm 0}, clip, width=\textwidth]{t_4p5min.jpg}
        		\caption*{$t=4.5$min}
        		\label{fig:Experiment_ogm_t4p5}
    	\end{subfigure}
	}
\end{figure}

\begin{frame}
\frametitle{Flying Vehicle in a Large Office-Like Environment}
\begin{itemize}
        	\item Hardware
	\begin{itemize}
		\item NVIDIA Jetson Ubuntu computer-on-module
		\item Asus Xtion IR color depth sensor
		\item Hokuyo LIDAR
		\item VectorNav IMU
	\end{itemize}
	\item Software
	\begin{itemize}
		\item Robot Operating System (ROS)
		\item Vicon Tracker (mocap\_vicon)
		\item Geometric Control: coordinate-free attitude control
	\end{itemize}
\end{itemize}
\begin{figure}
  \centering
  \begin{subfigure}[t]{.4\linewidth}
    \centering\includegraphics[height=.5\linewidth]{quad_top.png}
    \caption*{Quadrotor Top}
  \end{subfigure}
  \begin{subfigure}[t]{.4\linewidth}
    \centering\includegraphics[height=.5\linewidth]{quad_bottom.png}
    \caption*{Quadrotor Bottom}
  \end{subfigure}
\end{figure}
\end{frame}

% TODO: uncomment!
%\begin{frame}
%\frametitle{Large Flight Test Experiment Video}
%
%
%	\centering{
%		\includemedia[
%  		width=0.720\textwidth,
%  		height=0.576\textwidth,
%  		activate=pageopen,
%  		addresource=nrl_experiment_narrated.mp4,
%  		flashvars={source=nrl_experiment_narrated.mp4}
%		]{}{VPlayer.swf}
%		}
%
%
%\end{frame}

\begin{frame}
\frametitle{Flying Vehicle in a Complex 3D Environment}
\begin{itemize}
        	\item Full 3D mapping and exploration
	\item Objects are not vertically-uniform
\end{itemize}

\begin{figure}
  \centering
  \begin{subfigure}[t]{.4\linewidth}
    \centering\includegraphics[height=.7\linewidth]{explore3D_space_NW.JPG}
    \caption*{Northwest View}
  \end{subfigure}
  \begin{subfigure}[t]{.4\linewidth}
    \centering\includegraphics[height=.7\linewidth]{explore3D_space_NE.JPG}
    \caption*{Northeast View}
  \end{subfigure}
\end{figure}
\end{frame}

% TODO: uncomment! and update!
%\begin{frame}
%\frametitle{Full 3D Flying Experiment Video}
%
%
%	\centering{
%		\includemedia[
%  		width=0.720\textwidth,
%  		height=0.576\textwidth,
%  		activate=pageopen,
%  		addresource=gwu_experiment_narrated.mp4,
%  		flashvars={source=gwu_experiment_narrated.mp4}
%		]{}{VPlayer.swf}
%		}
%
%
%\end{frame}

\begin{frame}
\frametitle{Experiment Conclusions}
\begin{itemize}
        	\item Experimental environments in 2D and 3D are modeled with occupancy grids
	\item Future entropy prediction and collision-free regions use these occupancy probabilities
	\item A geometric controller is used during flight testing to follow the collision-free trajectory
	\item All algorithms are run in real-time without expensive post-processing 
\end{itemize}
\end{frame}

\section*{}
\subsection*{Conclusions and Publications}

\begin{frame}
\frametitle{Conclusions}
\begin{itemize}
        	\item Proposed an occupancy grid mapping technique that uses the \emph{exact probabilistic solution}
	\item Computational cost is reduced \emph{substantially} for \emph{real-time implementation} using probabilisitic properties and exploiting mathematical patterns
	\item Exact mapping concepts are extended to map uncertainty to accomplish \emph{autonomous exploration}
	\item Multiple vehicles can explore and patrol an uncertain environment using a \emph{bidding}-based approach
	\item These are demonstrated with numerous simulations and experiments
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Future Directions}
	\begin{itemize}
		\item Localization: use probabilistic map and other onboard sensors to localize, thereby completing the SLAM problem with the novel mapping approach
		\item Computational improvements: determine collision-free costs more efficiently than Dijkstra's cost map
		\item Decentralize the algorithms so processes may be distributed among multiple agents
	\end{itemize}
\end{frame}
